Quantitative Evaluation of Touch-Screen Performance with Transition Matrix Measures

### 2015-08-25 flux-entropy-paper/flux-entropy-paper.tex
a few extra words

>>>>

\section{A Corpus of Musical Touch-Screen Interactions}

In the following sections, we will use transition matrices, flux, and
entropy to analyse a corpus of data collected as part of our research
into collaborative interactions with musical touch-screen tablet
interfaces. In a period of more than two years (April 2013 - June 2015), we have
collected data from $135$ sessions where various participants used
musical touch-screen interfaces on Apple iPad devices. These sessions
had a number of contexts including rehearsals, performances, lab study
sessions, classes, and casual demonstrations. Participants performed
free improvisations as well as written compositions, performed on
iPads alone and in setups of iPads and acoustic percussion
instruments. The median length of these sessions was 7:32 and the
median number of participants was four.
